### 2016-02-18 paper.tex
Add 'and' to heading
Elaborate on effects of virtual camber; resolves #27

\subsection*{Survey of Validation Data Usage}

@@

The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
of $C_D$ was observed. The power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
positive trend. The tendency of $C_P$ to continue increasing slightly could be
an effect of lower ``virtual camber''---or flow curvature
\cite{Migliore1980}---when compared to the strong $Re$-independence of the
higher $c/R$ UNH-RVAT \cite{Bachant2016-RVAT-Re-dep}.

>>>>

\subsection*{Survey of Validation Data and Usage}

@@

The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
of $C_D$ was observed. The power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
positive trend. The tendency of $C_P$ to continue increasing slightly could be
an effect of flow curvature---caused by the finite $c/R$---which imparts a
``virtual camber'' \cite{Migliore1980}, or can be thought of as producing a
``lead'' in angle of attack since cambered airfoils have non-zero lift at zero
angle of attack \cite{Goude2012}. The weaker $Re$-independence of the RM2
compared to that of the higher $c/R$ UNH-RVAT could be due to this virtual
camber effect, since camber has been shown to cause earlier $Re$-convergence of
the CFT's geometric torque coefficient when calculated from static foil
coefficients given by a viscous panel method, whereas characteristics like
lift-to-drag ratio do not converge as strongly \cite{Bachant2016-RVAT-Re-dep}.
